---
title: "Extremely predictable cases"
output: html_notebook
---

Let's consider 4 different cases, where we can calculate a cdf of long run length.

1. Tossing a fair coin 10 000 times with probability of success $\frac{1}{2}$(Heads received). 
Calculating a cdf of the longest run length:
```{r}
library(plotly)
library(ggplot2)
# function to calculate cdf.
longest_run_distribution <- function(p, n){
  mean = 0 
  E <- function(x){-(p^x) * exp(-(p^x)) * log(p, exp(1))}
  find_area <- function(l){
    lower_bound = l - log(n*(1-p), 1/p)
    upper_bound = lower_bound + 1
    area = integrate(E, lower_bound, upper_bound) 
    return(area[["value"]])
  }
  probabilities <- vector()
  labels <- vector()
  for(l in 1:n){
    area = find_area(l)
    
    # calculating mean
    mean = mean + area * l
    
    if(area > 0.001){
      probabilities <- c(probabilities, area)
      labels <- c(labels, toString(l))
    }
  }
  print("Mean:")
  print(mean)
  
  # plotting
  df <- data.frame(text=labels,
                  num=probabilities)
  
      plot_ly(data = df,
       x = ~text,
       y = ~num,
       type = "bar",
       color = I("darkgreen")
  ) %>%
  layout(
       title = "Distribution of the longest run lenghts",
       xaxis = list(title = "Length of the longest run",
       categoryorder = "array",
       categoryarray = ~text),
       yaxis = list(title = "Probability", range = c(0,max(probabilities)))
  )
}

longest_run_distribution(1/2, 10000)
```
2. Rolling a fair die 10 000 times with probability of success $\frac{1}{6}$(side with number 3 rolled). 
Calculating a cdf of the longest run length:
```{r}
longest_run_distribution(1/6, 10000)
```
3. Generating a random digit 10 000 times with probability of success $\frac{1}{10}$(number 1 obtained). 
Calculating a cdf of the longest run length:
```{r}
longest_run_distribution(1/10, 10000)
```
4. Choosing a card from a deck of 32 cards 10 000 times(with returning the card back) with probability of success $\frac{1}{32}$(ace of spades is chosen). 
Calculating a cdf of the longest run length:
```{r}
longest_run_distribution(1/32, 10000)
```
As we can see, the smaller the value of p, the more concentrated the approximating extreme value
density becomes, and thus the length of the longest success run becomes even more
predictable.
